Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-06-10 manuscript/supplement.tex
Report effect sizes from bootstrap distributions in tables, too
Flag models that were not tested for significance
Adds a caret to models that were not tested for significance compared to the
naive model. These are only models for natural populations. This commit also
adds a missing bootstrap test for the epitope ancestor model of the simulated
populations.

\begin{table}[H]
  \begin{center}
    \scalebox{0.9}{
        \input{tables/complete_natural_model_selection.tex}
    }
    \caption{
      All model coefficients and performance on validation and test data for natural populations ordered from best to worst by distance to the future, as in Table~\ref{table_simulated_model_selection}.
      Distances annotated with asterisks (*) were significantly closer to the future than the naive model as measured by bootstrap tests (see Methods and Supplemental Fig.~\ref{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}).
      Validation results are based on 23 timepoints.
      Test results are based on eight timepoints not observed during model training and validation.
      Model results for additional variants of fitness metrics including those based on epitope mutations and DMS preferences are included for reference.
    }
    \label{sup_table:complete_natural_model_selection}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \scalebox{0.8}{
        \input{tables/composite_vs_individual_model_comparison.tex}
    }
    \caption{
      Comparison of composite and individual model distances to the future by bootstrap test (see Methods).
      Empirical differences represent the mean difference between the composite and individual models' distances to the future at each timepoint.
      The p values represent the proportion of n=10,000 bootstrap samples where the mean difference was greater than or equal to zero.
    }
    \label{sup_table:composite_vs_individual_model_comparison}
  \end{center}
\end{table}

>>>>

\begin{table}[H]
  \begin{center}
    \scalebox{0.9}{
        \input{tables/complete_natural_model_selection.tex}
    }
    \caption{
      All model coefficients and performance on validation and test data for natural populations ordered from best to worst by distance to the future, as in Table~\ref{table_simulated_model_selection}.
      Distances annotated with asterisks (*) were significantly closer to the future than the naive model as measured by bootstrap tests (see Methods and Supplemental Fig.~\ref{sup_fig:bootstrap_distributions_for_natural_sample_1_with_90_vpm_sliding}).
      Distances annotated with carets ($\wedge$) were not tested for significance relative to the naive model.
      Validation results are based on 23 timepoints.
      Test results are based on eight timepoints not observed during model training and validation.
      Model results for additional variants of fitness metrics including those based on epitope mutations and DMS preferences are included for reference.
    }
    \label{sup_table:complete_natural_model_selection}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \scalebox{0.7}{
        \input{tables/composite_vs_individual_model_comparison.tex}
    }
    \caption{
      Comparison of composite and individual model distances to the future by bootstrap test (see Methods).
      The effect size of differences between models in amino acids is given by the mean and standard deviation of the bootstrap distributions.
      The p values represent the proportion of n=10,000 bootstrap samples where the mean difference was greater than or equal to zero.
    }
    \label{sup_table:composite_vs_individual_model_comparison}
  \end{center}
\end{table}
